Prefetching SPARQL query cacher

### 2016-08-03 dissertation/cache-proxy.tex
Shorten test.invalid to ex.org

Following this discussion, consider this example:
\begin{example}{A four-triple pattern BGP}\label{ex:bgp4}
\begin{verbatim}
?s <http://ex.org/p> "1" .                      # A
?s <http://ex.org/q> <http://ex.org/a> . # B
?s <http://ex.org/p> ?o .                       # C
?o <http://ex.org/b> "2" .                      # D
\end{verbatim}
\end{example}
Say that the first triple pattern has a result in the cache. This will
not cause Problem~\ref{prob:cachecartesian} to occur (it would have
occurred if the third triple pattern had a cached result, however), so
we can safely use the cache. The results of the three remaining triple
patterns must be fetched from a remote server. There are essentially
two reasonable choices: Either fetch the result from an LDF server as
argued by \cite{verborgh2014querying} and join them locally or send a
single, rewritten SPARQL query to the remote endpoint for the
evaluation. When the results are returned from both the cache and the
remote endpoint, they must then finally be joined to produce the final
result returned to the client. A string representation of the plan
tree from the current implementation reflects this and reads (note
that accessing the cache is represented by an iterator plan):
\begin{example}{An example Attean plan with a remotely executed BGP}
\begin{verbatim}
- Hash Join { s } (distinct cost: 74)
-   SPARQLBGP (cost: 60)
-     Quad { ?s, <http://ex.org/p>, ?o, <http://test.invalid/graph> }
-     Quad { ?o, <http://ex.org/b>, "2", <http://test.invalid/graph> }
-     Quad { ?s, <http://ex.org/q>, <http://ex.org/a>, <http://test.invalid/graph> }
-   Iterator (?s with 2 elements) (cost: 2)
\end{verbatim}
\end{example}

>>>>

Following this discussion, consider this example:
\begin{example}{A four-triple pattern BGP}\label{ex:bgp4}
\begin{verbatim}
?s <http://ex.org/p> "1" .                      # A
?s <http://ex.org/q> <http://ex.org/a> . # B
?s <http://ex.org/p> ?o .                       # C
?o <http://ex.org/b> "2" .                      # D
\end{verbatim}
\end{example}
Say that the first triple pattern has a result in the cache. This will
not cause Problem~\ref{prob:cachecartesian} to occur (it would have
occurred if the third triple pattern had a cached result, however), so
we can safely use the cache. The results of the three remaining triple
patterns must be fetched from a remote server. There are essentially
two reasonable choices: Either fetch the result from an LDF server as
argued by \cite{verborgh2014querying} and join them locally or send a
single, rewritten SPARQL query to the remote endpoint for the
evaluation. When the results are returned from both the cache and the
remote endpoint, they must then finally be joined to produce the final
result returned to the client. A string representation of the plan
tree from the current implementation reflects this and reads (note
that accessing the cache is represented by an iterator plan):
\begin{example}{An example Attean plan with a remotely executed BGP}
\begin{verbatim}
- Hash Join { s } (distinct cost: 74)
-   SPARQLBGP (cost: 60)
-     Quad { ?s, <http://ex.org/p>, ?o, <http://ex.org/graph> }
-     Quad { ?o, <http://ex.org/b>, "2", <http://ex.org/graph> }
-     Quad { ?s, <http://ex.org/q>, <http://ex.org/a>, <http://ex.org/graph> }
-   Iterator (?s with 2 elements) (cost: 2)
\end{verbatim}
\end{example}
